### 2014-06-20 dicook/map.Rmd
first draft of a map

```{r usefulfn}
library(plyr)
extractPolygons <- function(shapes) {

@@

# To get a blank background on map
new_theme_empty <- theme_bw()
new_theme_empty$line <- element_blank()
new_theme_empty$rect <- element_blank()
new_theme_empty$strip.text <- element_blank()
new_theme_empty$axis.text <- element_blank()
new_theme_empty$plot.title <- element_blank()
new_theme_empty$axis.title <- element_blank()
new_theme_empty$plot.margin <- structure(c(0, 0, -1, -1), unit = "lines", valid.unit = 3L, class = "unit")

```

```{r maps}
# Extract map polygons for modern world
world <- getMap(resolution = "low")
world.polys <- extractPolygons(world)
detach("package:plyr")
# Subset data
student2012.sub <- student2012[, c(1:7, 500:550)]
colnames(student2012.sub)[1] <- "name"
student2012.sub$name <- as.character(student2012.sub$name)
# Check mismatches of names
unique(anti_join(student2012.sub, world.polys)[1])
student2012.sub$name[student2012.sub$name=="Serbia"] <- "Republic of Serbia"
student2012.sub$name[student2012.sub$name=="Korea"] <- "South Korea"
student2012.sub$name[student2012.sub$name=="Chinese Taipei"] <- "Taiwan"
student2012.sub$name[student2012.sub$name=="Slovak Republic"] <- "Slovakia"
student2012.sub$name[student2012.sub$name=="Russian Federation"] <- "Russia"
student2012.sub$name[student2012.sub$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
student2012.sub$name[student2012.sub$name=="China-Shanghai"] <- "China"

student2012.sub.map <- left_join(student2012.sub, world.polys)
unique(student2012.sub$name)
qplot(X1, X2, order=order, group=group, data=student2012.sub.map, geom="polygon", fill=PropBoys) + new_theme_empty

```

>>>>

```{r usefulfn}
extractPolygons <- function(shapes) {

@@

# To get a blank background on map
new_theme_empty <- theme_bw()
new_theme_empty$line <- element_blank()
new_theme_empty$rect <- element_blank()
new_theme_empty$strip.text <- element_blank()
new_theme_empty$axis.text <- element_blank()
new_theme_empty$plot.title <- element_blank()
new_theme_empty$axis.title <- element_blank()
new_theme_empty$plot.margin <- structure(c(0, 0, -1, -1), unit = "lines", valid.unit = 3L, class = "unit")
```

```{r maps, fig.width=12, fig.height=7}
# Extract map polygons for modern world
world <- getMap(resolution = "low")
library(plyr)
world.polys <- extractPolygons(world)
detach("package:plyr")
# Subset data
student2012.sub <- student2012[, c(1:7, 500:550)]
colnames(student2012.sub)[1] <- "name"
student2012.sub$name <- as.character(student2012.sub$name)
# Check mismatches of names
unique(anti_join(student2012.sub, world.polys)[1])
student2012.sub$name[student2012.sub$name=="Serbia"] <- "Republic of Serbia"
student2012.sub$name[student2012.sub$name=="Korea"] <- "South Korea"
student2012.sub$name[student2012.sub$name=="Chinese Taipei"] <- "Taiwan"
student2012.sub$name[student2012.sub$name=="Slovak Republic"] <- "Slovakia"
student2012.sub$name[student2012.sub$name=="Russian Federation"] <- "Russia"
student2012.sub$name[student2012.sub$name=="Hong Kong-China"] <- "Hong Kong S.A.R."
student2012.sub$name[student2012.sub$name=="China-Shanghai"] <- "China"

# Only need one of the plausible values, checked they are effectively identical
student2012.sub$PV1MATH <- as.numeric(student2012.sub$PV1MATH)
student2012.sub$PV1MACC <- as.numeric(student2012.sub$PV1MACC)
student2012.sub$PV1MACQ <- as.numeric(student2012.sub$PV1MACQ)
student2012.sub$PV1MACS <- as.numeric(student2012.sub$PV1MACS)
student2012.sub$PV1MACU <- as.numeric(student2012.sub$PV1MACU)
student2012.sub$PV1MAPE <- as.numeric(student2012.sub$PV1MAPE)
student2012.sub$PV1MAPF <- as.numeric(student2012.sub$PV1MAPF)
student2012.sub$PV1MAPI <- as.numeric(student2012.sub$PV1MAPI)
student2012.sub.math <- summarise(group_by(student2012.sub[,c(1,seq(9,48,5))], name), math=mean(PV1MATH), mCC=mean(PV1MACC), 
                                  mCQ=mean(PV1MACQ), mCS=mean(PV1MACS), mCU=mean(PV1MACU), mPE=mean(PV1MAPE), 
                                  mPF=mean(PV1MAPF), mPI=mean(PV1MAPI))
#pairs(student2012.sub.math[,-1])

# Left join to only get countries that are measured
student2012.sub.map <- left_join(student2012.sub.math, world.polys)
#qplot(X1, X2, order=order, group=group, data=student2012.sub.map, geom="polygon", fill=math) + coord_map() + new_theme_empty

# Really need all boundaries, doesn't quite work to have boundaries with one data: coord_map is the problem
ggplot(data=world.polys) + geom_path(aes(x=X1, y=X2, order=order, group=group), colour=I("grey70")) + 
  geom_polygon(data=student2012.sub.map, aes(x=X1, y=X2, order=order, group=group, fill=math)) +
#  coord_map() + 
  new_theme_empty + theme(legend.position="none")

# Join to get missings for countries that are not measured
#student2012.sub.map <- merge(student2012.sub.math, world.polys, all.y=TRUE)
#qplot(X1, X2, order=order, group=group, data=student2012.sub.map, geom="polygon", fill=math, colour=I("grey70")) + 
  #coord_map(xlim=c(-195, 185), ylim=c(-150, 95)) + # Having trouble getting coord_map to not cut off polygons weirdly
#  new_theme_empty + theme(legend.position="none")
```
